---
title: "SERDP_datacleaning"
author: "Jake Eisaguirre"
date: "7/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse, here, parsedate, lubridate, janitor, stringr, parsedate) #plyr package breaks a lot of tidyverse pacakages
```


# site_level data - this code chunk is `ugly AF` need to create loop for this!
```{r, messages=F}
# # all 2017 site level data
# site_level_data_2017 <- read_csv(here::here("data", "site_level_data", "2017_site_data", 
#                                       "site_level_data_2017_all.csv")) %>% 
#   clean_names() %>% 
#   mutate(date = parse_date(date), #parse data to iso 8601
#          end_time = parse_time(end_time),
#          start_time = parse_time(start_time))
  
# 2018 site level data
site_level_data_2018_LA <- read_csv(here::here("data", "site_level_data", "2018_site_data", "LA_site_2018.csv")) %>%
  clean_names() %>% 
  mutate(date = parse_date(date))
site_level_data_2018_NM <- read_csv(here::here("data", "site_level_data", "2018_site_data", "NM_site_2018.csv"))  %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2018_PA <- read_csv(here::here("data", "site_level_data", "2018_site_data", "PA_site_2018.csv")) %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2018_TN <- read_csv(here::here("data", "site_level_data", "2018_site_data", "TN_site_2018.csv")) %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2018_VT <- read_csv(here::here("data", "site_level_data", "2018_site_data", "VT_site_2018.csv")) %>% 
  clean_names() %>%
  mutate(date = parse_date(date))

# 2019 site level data
site_level_data_2019_LA <- read_csv(here::here("data", "site_level_data", "2019_site_data", "LA_site_2019.csv")) %>%
  clean_names() %>% 
  mutate(date = parse_date(date))

site_level_data_2019_NM <- read_csv(here::here("data", "site_level_data", "2019_site_data", "NM_site_2019.csv"))  %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2019_PA <- read_csv(here::here("data", "site_level_data", "2019_site_data", "PA_site_2019.csv")) %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2019_TN <- read_csv(here::here("data", "site_level_data", "2019_site_data", "TN_site_2019.csv")) %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2019_VT <- read_csv(here::here("data", "site_level_data", "2019_site_data", "VT_site_2019.csv")) %>% 
  clean_names() %>%
  mutate(date = parse_date(date))

# 2017 site level data
site_level_data_2017_LA <- read_csv(here::here("data", "site_level_data", "2017_site_data", "LA_site_2017.csv")) %>%
  clean_names() %>% 
  mutate(date = parse_date(date))

site_level_data_2017_NM <- read_csv(here::here("data", "site_level_data", "2017_site_data", "NM_site_2017.csv"))  %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2017_PA <- read_csv(here::here("data", "site_level_data", "2017_site_data", "PA_site_2017.csv")) %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2017_TN <- read_csv(here::here("data", "site_level_data", "2017_site_data", "TN_site_2017.csv")) %>%
  clean_names() %>%
  mutate(date = parse_date(date))

site_level_data_2017_VT <- read_csv(here::here("data", "site_level_data", "2017_site_data", "VT_site_2017.csv")) %>% 
  clean_names() %>%
  mutate(date = parse_date(date))
```

# combine data sets 
```{r}
# rbin all site level including non-matched columns
site_level_data <- as.data.frame(plyr::rbind.fill(site_level_data_2018_LA, 
                                      site_level_data_2018_NM, site_level_data_2018_PA,
                                      site_level_data_2018_TN, site_level_data_2018_VT,
                                      site_level_data_2019_LA, 
                                      site_level_data_2019_NM, site_level_data_2019_PA,
                                      site_level_data_2019_TN, site_level_data_2019_VT,
                                      site_level_data_2017_NM, site_level_data_2017_PA,
                                      site_level_data_2017_TN, site_level_data_2017_VT,
                                      site_level_data_2017_LA)) %>% 
  mutate(site_code = as.numeric(site_code))
  

# read in site_coordinates
site_coords <- read_csv(here::here('data', "site_level_data", "site_coordinates.csv")) %>% 
  clean_names() %>% 
  mutate(site_code = as.numeric(substring(site, 3)),
         site = str_to_lower(substring(site, 1,2)),
         site = paste(site, site_code, sep = "")) %>% 
  select(!site_code) %>% 
  mutate(dod_location = str_to_lower(dod_location))


#write_csv(site_coords, here::here("clean_tables", "site_codes.csv"))
  
#join all site_level data on "dod_location" and "site_code"
#site_level_data <- left_join(site_level_data, site_coords, by = c("dod_location", "site_code"))


write_csv(site_level_data, here::here("clean_tables", "all_site_level_data.csv"))


```

# now pull out site table on unique sites
```{r}

site_table <- site_level_data %>% 
  mutate(site_code = as.numeric(site_code)) %>% 
  dplyr::select(dod_location, site_code) %>% 
  mutate(site = paste(dod_location, site_code, sep = "")) %>% 
  dplyr::group_by(dod_location, site_code) %>% 
  dplyr::mutate(site_temp_id = cur_group_id(),
                dod_location = str_to_lower(dod_location),
                site = str_to_lower(site),
                site_code = str_to_lower(site_code))%>% 
  dplyr::filter(!duplicated(site_temp_id)) %>% 
  full_join(site_coords, by = c('site', 'dod_location')) %>% 
  select(!c(site_temp_id))
  

write_csv(site_table, here::here("clean_tables", "site_table.csv"))

```

# pull out regions
```{r}
region_tabl <- site_table %>% 
  select(dod_location, site_code) %>% 
  group_by(dod_location) %>% 
  mutate(temp_reg_id = cur_group_id()) %>% 
  filter(!duplicated(temp_reg_id)) %>% 
  select(!site_code) %>% 
  drop_na()

write_csv(region_tabl, here("clean_tables", "region_table.csv"))

```


# now pull out location on unique locatins
```{r}

# location_table <- site_table %>% 
#   ungroup() %>% 
#   dplyr::select(dod_location) %>%
#   group_by(dod_location) %>% 
#   dplyr::mutate(location = str_to_lower(dod_location),
#          temp_loc_id = cur_group_id()) %>% 
#   dplyr::filter(!duplicated(temp_loc_id)) %>% 
#   ungroup() %>% 
#   dplyr::select(!c("dod_location"))
# 
# write_csv(location_table, here::here("clean_tables", "location_table.csv"))

```


# now pull out unique visists based on date and survey time - SEE BELOW FOR TRUE VISIST TABLE
```{r}

visit_table <- site_level_data %>% 
  ungroup() %>% 
  select(date, survey_time, site_code, dod_location) %>% 
  group_by(date, survey_time, site_code, dod_location) %>%
  dplyr::mutate(temp_visit_id = cur_group_id(),
                survey_time = str_to_lower(survey_time),
                dod_location = str_to_lower(dod_location),
                date = parse_date(date)) %>%
  dplyr::filter(!duplicated(temp_visit_id))

t <- visit_table %>% 
  ungroup() %>% 
  count(date, dod_location, site_code, survey_time) %>% 
  filter(n>1)


write_csv(visit_table, here::here("clean_tables", "visit_table.csv"))

```

```{r}
all_db_visit_table <- visit_table %>% 
  unite(site_code, dod_location:site_code, sep = "") %>% 
  left_join(site_coords, by = c("site_code" = "site")) %>% 
  select(!c(temp_visit_id, dod_location, lat, long, notes))

write_csv(all_db_visit_table, here("clean_tables", "serdp_visit.csv"))
```


# now create survey table - SEE BELOW FOR TRUE SURVEY TABLE
```{r}

survey_table <- site_level_data %>% 
  ungroup() %>% 
  mutate(dod_location = str_to_lower(dod_location)) %>% 
  unite(site_code, c(dod_location, site_code), sep="") %>% 
  full_join(site_coords, by = c("site_code" = "site")) %>% 
  rename(densiometer_d1_num_covered=densiometer_d1_num_covered_uncovered) %>% 
  rename(densiometer_d2_num_covered=densiometer_d2_num_covered_uncovered) %>% 
  group_by(date, site_code, survey_time) %>% 
  mutate(temp_survey_id = cur_group_id(),
         investigator_i_ds = str_to_lower(investigator_i_ds),
         vegetation_notes = str_to_lower(vegetation_notes),
         weather_condition_notes = str_to_lower(weather_condition_notes),
         survey_time = str_to_lower(survey_time),
         precipitation_during_visit = str_to_lower(precipitation_during_visit),
         temperature_last_48_h = str_to_lower(temperature_last_48_h),
         densiometer_d1_num_covered = case_when(densiometer_d1_num_covered == "covered" ~ 1,
                                                densiometer_d1_num_covered == "uncovered" ~ 0),
         densiometer_d2_num_covered = case_when(densiometer_d2_num_covered == "covered" ~ 1,
                                                densiometer_d2_num_covered == "uncovered" ~ 0),
         e_dna_sample = if_else(e_dna_sample == "Y", 1, 0)) %>% 
  select(!c("dod_location",site_name.x, dod_site_location_name, site_acronym, lat.x, long.x, dod_location, site_name.y, lat.y, long.y, notes.y,
            site_code_notes)) %>% 
  rename(survey_notes = notes.x) %>% 
   filter(!duplicated(temp_survey_id))



t <- survey_table %>% 
  ungroup() %>% 
  count(date, site_code, survey_time) %>% 
  filter(n>1)

write_csv(survey_table, here::here("clean_tables", "survey_table.csv"))

```


# read in animal data - now that is how the above code chunk should look, `me gusta`
```{r}

# tn
file_path <- here::here(here::here("data", "animal_level_data", "tn"), 
                        list.files(here::here("data", "animal_level_data", "tn"), pattern = "*.csv"))


tn <- lapply(file_path, read.csv)
tn_1 <- plyr::rbind.fill(tn) %>% 
  clean_names() %>% 
  select(!c(bd_total, infected, entry))



# vt
file_path <- here::here(here::here("data", "animal_level_data", "vt"), 
                        list.files(here::here("data", "animal_level_data", "vt"), pattern = "*.csv"))

vt <- lapply(file_path, read.csv)
vt_1 <- plyr::rbind.fill(vt) %>% 
  clean_names() %>% 
  select(!c(capture_number))

# pa
file_path <- here::here(here::here("data", "animal_level_data", "pa"), 
                        list.files(here::here("data", "animal_level_data", "pa"), pattern = "*.csv"))

pa <- lapply(file_path, read.csv)
pa_1 <- plyr::rbind.fill(pa) %>% 
  clean_names() %>% 
  select(!c(column22)) %>% 
  unite("column2", c("column2", "column23"), sep = "", na.rm = T) %>% 
  unite("notes", c("column2", "notes"), sep = "", na.rm = T) %>% 
  unite("notes", c("column4", "notes"), sep = "", na.rm = T) %>% 
  unite("buckets", c("buckets", "buchet_number"), sep = "", na.rm = T)

# la
file_path <- here::here(here::here("data", "animal_level_data", "la"), 
                        list.files(here::here("data", "animal_level_data", "la"), pattern = "*.csv"))

la <- lapply(file_path, read.csv)
la_1 <- plyr::rbind.fill(la) %>% 
  clean_names() %>% 
  unite("number_of_mites", c("number_of_mites", "number_of_mites_2"), sep="", na.rm=T)

# nm
file_path <- here::here(here::here("data", "animal_level_data", "nm"), 
                        list.files(here::here("data", "animal_level_data", "nm"), pattern = "*.csv"))

nm <- lapply(file_path, read.csv)
nm_1 <- plyr::rbind.fill(nm) %>% 
  clean_names() %>% 
  select(!c(species_code_1))

all_bio_data <- plyr::rbind.fill(pa_1, tn_1, vt_1, la_1, nm_1) %>% 
  clean_names() %>% 
  select(!c(site_name, serdp_location_name)) %>% 
  unite("temp_gun", c("temp_gun", "temp_gun_number"), sep="", na.rm = T)


# site_code and date join on for P.key
capture_table <- all_bio_data %>% 
  dplyr::mutate(temp_capture_id = row_number(),
                dod_location = str_to_lower(dod_location),
                site_code = str_to_lower(site_code),
                microhabitat_notes = str_to_lower(microhabitat_notes),
                microhabitat_category = str_to_lower(microhabitat_category),
                sex = str_to_lower(sex),
                life_stage = str_to_lower(life_stage),
                survey_time = str_to_lower(survey_time),
                notes = str_to_lower(notes),
                date = parse_date(date)) %>% 
  select(!c(site)) %>% 
  mutate(bd_swab = case_when(bd_swab == "Y" ~ 1,
                             bd_swab == "N" ~ 0),
         mucosome = case_when(mucosome == "Y" ~ 1,
                              mucosome == "N" ~ 0),
         microbiome = case_when(microbiome =="Y" ~ 1,
                                microbiome == "N" ~ 0),
         am_ps = case_when(am_ps == "Y" ~ 1,
                           am_ps == "N" ~ 0),
         antibodies = case_when(antibodies == "Y" ~ 1,
                                antibodies == "N" ~ 0))

write_csv(capture_table, here::here("clean_tables", "capture_table.csv"))

```

# get site info from capture table - TRUE SITE AND VISIT TABLE
```{r}

cap_site_info <- all_bio_data %>% 
  select(date, survey_time, dod_location, site_code) %>% 
  mutate(date = parse_date(date))

site_info <- site_level_data %>% 
  select(date, survey_time, dod_location, site_code) %>% 
  na.omit()


### TRUE SITE TABLE

true_site_table <- cap_site_info %>% 
  rbind(site_info) %>% 
  mutate(dod_location = str_to_lower(dod_location)) %>% 
  unite(site, dod_location:site_code, sep = "") %>% 
  full_join(site_coords, by = c('site')) %>% 
  rename(site_code = site,
         site = site_name) %>% 
  select(!c(survey_time, date)) %>% 
  group_by(site_code) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(!duplicated(temp_id))

write_csv(true_site_table, here("clean_tables", "site_table.csv"))




### TRUE VISIST TABLE

true_visit_table <- cap_site_info %>% 
  rbind(site_info) %>% 
  dplyr::select(dod_location, site_code, date, survey_time) %>% 
  mutate(site = paste(dod_location, site_code, sep = "")) %>% 
  dplyr::group_by(dod_location, site_code, date) %>% 
  dplyr::mutate(site_temp_id = cur_group_id(),
                dod_location = str_to_lower(dod_location),
                site = str_to_lower(site),
                site_code = str_to_lower(site_code))%>% 
  dplyr::filter(!duplicated(site_temp_id)) %>% 
  full_join(site_coords, by = c('site', 'dod_location')) %>%
  ungroup() %>% 
  select(!c(site_temp_id, site_code, dod_location, lat, long)) %>% 
  rename(temp = site,
         site= site_name) %>% 
  rename(site_code = temp)

t <- visit_table %>% 
  ungroup() %>% 
  count(date, dod_location, site_code, survey_time) %>% 
  filter(n>1)

write_csv(true_visit_table, here("clean_tables", "visit_table.csv"))


### TRUE SURVEY TABLE

true_survey_table <- plyr::rbind.fill(site_level_data, cap_site_info) %>% 
  unite(site_code, c(dod_location, site_code), sep="") %>% 
   group_by(date, site_code, survey_time) %>% 
  dplyr::mutate(temp_survey_id = cur_group_id(),
                investigator_i_ds = str_to_lower(investigator_i_ds),
                vegetation_notes = str_to_lower(vegetation_notes),
                weather_condition_notes = str_to_lower(weather_condition_notes),
                site_code = str_to_lower(site_code),
                precipitation_last_48_h = str_to_lower(precipitation_last_48_h),
                survey_time = str_to_lower(survey_time),
                precipitation_during_visit = str_to_lower(precipitation_during_visit),
                temperature_last_48_h = str_to_lower(temperature_last_48_h),
                date = parse_date(date)) %>% 
  filter(!duplicated(temp_survey_id)) %>% 
  rename(densiometer_d1_num_covered=densiometer_d1_num_covered_uncovered) %>% 
  rename(densiometer_d2_num_covered=densiometer_d2_num_covered_uncovered) %>% 
  mutate(densiometer_d1_num_covered = case_when(densiometer_d1_num_covered == "covered" ~ 1,
                                                densiometer_d1_num_covered == "uncovered" ~ 0),
         densiometer_d2_num_covered = case_when(densiometer_d2_num_covered == "covered" ~ 1,
                                                densiometer_d2_num_covered == "uncovered" ~ 0),
         e_dna_sample = case_when(e_dna_sample == "Y" ~ 1,
                                  e_dna_sample == "N" ~ 0)) %>% 
  select(!c(site_code_notes, temp_survey_id, site_acronym, lat, long, )) %>% 
  rename(survey_notes = notes)

write_csv(true_survey_table, here("clean_tables", "survey_table.csv"))

```


# read in qPCR data
```{r}


qpcr_2017 <- read_csv(here("data", "qPCR_results", "SERDP qPCR results 2017_220721.csv")) %>% 
  clean_names()

qpcr_2018 <- read_csv(here("data", "qPCR_results", "SERDP qPCR results 2018_191129.csv")) %>% 
  clean_names()

qpcr_2019 <- read_csv(here("data", "qPCR_results", "SERDP qPCR results 2019_220721.csv")) %>% 
  clean_names()

all_qpcr <- plyr::rbind.fill(qpcr_2017, qpcr_2018, qpcr_2019)

q_pcr_table <- all_qpcr %>% 
  clean_names() %>% 
  group_by(sample_id) %>% 
  mutate(extract_date = parse_date(extract_date),
                qpcr_date = parse_date(qpcr_date),
         temp_pcr_id = cur_group_id()) %>% 
  filter(!duplicated(temp_pcr_id)) %>% 
  select(!c(species, site, temp_pcr_id, collect_site)) %>% 
  select(sample_id, extract_date, qpcr_date, qpcr_diluted, sample_quality, sample_ipc, sample_rerun, sample_bd,
         sample_bd_ct, sample_bd_qty, sample_bd_swab_qty, sample_bsal, sample_bsal_qty, sample_bsal_swab_qty, notes)

extra_qpcr_table <- all_qpcr %>% 
  clean_names() %>% 
  group_by(sample_id) %>% 
  mutate(temp_pcr_id = cur_group_id()) %>% 
  filter(!duplicated(temp_pcr_id)) %>% 
  select(!c(extract_date, qpcr_date, qpcr_diluted, sample_quality, sample_ipc, sample_rerun, sample_bd,
         sample_bd_ct, sample_bd_qty, sample_bd_swab_qty, sample_bsal, sample_bsal_qty, sample_bsal_swab_qty, notes, temp_pcr_id))


# q_pcr_table <- all_qpcr %>% 
#   clean_names() %>% 
#   group_by(sample_id, collect_site) %>% 
#   dplyr::mutate(temp_pcr_id = cur_group_id()) %>% 
#   filter(!duplicated(temp_pcr_id))
# 
# a <- q_pcr_table %>% 
#   count(sample_id) %>% 
#   filter(n>1)
# write_csv(a, here("sample_id_check.csv"))
# 
# q_p <- q_pcr_table %>% 
#   filter(sample_id %in% a$sample_id) %>% 
#   drop_na(sample_id) %>% 
#   filter(!sample_id == "NEG EXTRACT CONTROL",
#          !sample_id == "POS EXTRACT CONTROL")
# 
# write_csv(q_p, here("sample_id_check.csv"))

write_csv(q_pcr_table, here::here("clean_tables", "qpcr_table.csv"))
write_csv(extra_qpcr_table, here("clean_tables", "course_qpcr_table.csv"))
```

# hobo shade
```{r}

hobo_shade <- read_csv(here::here("data", "environmental_data", "Shade_HOBO_2021_01_28.csv")) %>% 
  clean_names()

hobo_shade_date <- hobo_shade %>% 
  mutate(date_time = parse_date_time(date_time, c("mdy H", "mdy HM", "mdy HMS", "mdy")))

shade_hobo <- hobo_shade_date %>% 
  mutate(dod_location = substr(site, 1,2),
         site = str_sub(site, 3),
         dod_location = str_to_lower(dod_location),
         site = as.numeric(site),
         date = format(as.Date(date_time), "%Y-%m-%d")) %>% 
  select(!c(x1, x))



write_csv(shade_hobo, here::here("clean_tables", "shade_hobo.csv"))

```

# hobo soil
```{r}

hobo_soil <- read_csv(here::here("data", "environmental_data", "Soil_HOBO_2021_01_28.csv")) %>% 
  clean_names()

hobo_soil_date <- hobo_soil %>% 
  mutate(date_time = parse_date_time(date_time, c("mdy H", "mdy HM", "mdy HMS", "mdy")))

soil_hobo <- hobo_soil_date %>% 
  mutate(dod_location = substr(site, 1,2),
         site = str_sub(site, 3),
         dod_location = str_to_lower(dod_location),
         site = as.numeric(site),
         date = format(as.Date(date_time), "%Y-%m-%d"))%>% 
  select(!c(x1, x))


write_csv(soil_hobo, here::here("clean_tables", "soil_hobo.csv"))

```

# hobo sun
```{r}

hobo_sun <- read_csv(here::here("data", "environmental_data", "Sun_HOBO_2021_01_28.csv")) %>% 
  clean_names()

hobo_sun_date <- hobo_sun %>% 
  mutate(date_time = parse_date_time(date_time, c("mdy H", "mdy HM", "mdy HMS", "mdy")))

sun_hobo <- hobo_sun_date %>% 
  mutate(dod_location = substr(site, 1,2),
         site = str_sub(site, 3),
         dod_location = str_to_lower(dod_location),
         site = as.numeric(site),
         date = format(as.Date(date_time), "%Y-%m-%d"))%>% 
  select(!c(x1, x))


write_csv(sun_hobo, here::here("clean_tables", "sun_hobo.csv"))

```

# water hobo
```{r}

hobo_water <- read_csv(here::here("data", "environmental_data", "Water_HOBO_2021_01_28.csv")) %>% 
  clean_names()

hobo_water_date <- hobo_water %>% 
  mutate(date_time = parse_date_time(date_time, c("mdy H", "mdy HM", "mdy HMS", "mdy")))

water_hobo <- hobo_water_date %>% 
  mutate(dod_location = substr(site, 1,2),
         site = str_sub(site, 3),
         dod_location = str_to_lower(dod_location),
         site = as.numeric(site),
         date = format(as.Date(date_time), "%Y-%m-%d"))%>% 
  select(!c(x1, x)) %>% 
  filter(!light == "Logged")


write_csv(water_hobo, here::here("clean_tables", "water_hobo.csv"))


```

# genomics data
```{r}

raw_gen <- read_csv(here("data", "SERDP_data_all_for_metaanalysis.csv")) %>% 
  clean_names()

gen <- raw_gen %>% 
  select(c(lab_code, seq_run, new_sample_id, sample_id, season, n_seqs_187, avg_alleles_per_locus, lineage_astral_187,
           lineage_dapc_2_99cut)) %>% 
  mutate(season = str_to_lower(season))

write_csv(gen, here("clean_tables", "genomics.csv"))

```

# newt AMP data
```{r}

raw_newt <- read_csv(here("data", "SERDPnewts_2017_2018_2019_Field_Bdinfo_Microbiome_Antifungal_TTX_Mucosome.csv")) %>% 
  select(c(SwabID, observed_features:Shedding_Infected)) %>% 
  clean_names()

write_csv(raw_newt, here("clean_tables", "microbiome_antifungal_TTX_mucosome.csv"))
```

